---
title: "GroupB_Final"
author: "S.Carpenè, G.Fantuzzi, V.Nigam, M.Tallone, A.Valentinis"
date: "2024-02-14"
output:
  html_document:
    toc: yes
    toc_depth: '3'
    df_print: paged
  pdf_document:
    toc: yes
    toc_depth: 3
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, echo=FALSE, warning=FALSE, message=FALSE}
# Loading all necessary libraries
library(car)
library(caret)
library(pROC)
library(forcats)

# Loading the utilities for assessment and plots
source("markdown_utils.r")
```

# Problem statement and dataset

The `BankChurners` dataset contains information about a bank's costumers and their credit card usage. The dataset is available on the Kaggle website and it is used for a classification problem. The main goal is to predict the `Attrition_Flag` response variable, which basically explains whether a customer will churn or not. The dataset consist of 10127 observations and 21 variables.

# Data preparation and EDA (Exploratory Data Analysis)

With the exclusion of the first variable (`CLIENTNUM`), that is just an identification number, and the last two (`Naive_Bayes_Classifier...`) variables, the dataset contains 19 possible covariates to be used for prediction. Among these, there are 6 categorical variables and 13 numerical variables.

The `Attrition_Flag` variable is the response variable and it is a binary variable. The dataset is unbalanced, with only 16.07% of the observations being positive, i.e. a churned costumer, for the `Attrition_Flag` variable.\

# Models implementation

## Logistic regression

The first model we build in the attempt of predicting the response variable has been a logistic regression model using the $logit$ link function.\
In the initial model we included all the covariates except those that had low correlation with the response variable. We further filtered the covariates selection by discarding the variables that had a $p-value$ higher than 0.05 in the `glm()` summary output, i.e. the variables that were not statistically significant in the prediction.\
Possible multicollinearity problems, especially among the variables that showed high correlation in the exploratory analysis, were checked by looking at the Variance Inflation Factor (VIF) of the covariates.\
The final model has been built using the following variables:

* `Gender`: the gender of the customer
* `Total_Relationship_Count`: the total number of products held by the customer
* `Months_Inactive_12_mon`: the number of months inactive in the last 12 months
* `Contacts_Count_12_mon`: the number of contacts in the last 12 months
* `Total_Revolving_Bal`: the total revolving balance on the credit card
* `Total_Trans_Amt`: the total transaction amount in the last 12 months
* `Total_Trans_Ct`: the total transaction count in the last 12 months
* `Total_Ct_Chng_Q4_Q1`: the change in transaction count from Q4 to Q1

Aditionally, looking at the data distribution it has been taken the logarihmic values of the `Total_Trans_Amt` variable. Also, the `Months_Inactive_12_mon` variable has been converted to a factor due to its peculiar distribution with the levels `1`, `2`, `3` and `4+` months.
Both these changes have significantly improved the model performance as portrayed by the metrics below. An ANOVA test has also been performed to check the significance of the model.

In order to assess the model performance, different effectiveness metrics have been used. These have been computed both by fitting the model using all the observations in the dataset and also by performing a k-fold cross validation with $k=10$. The metrics used are the following:

* Accuracy
* AUC
* FPR (False Positive Rate)
* FNR (False Negative Rate)
* Confusion matrix (*only in the whole dataset case*)
* AIC
* BIC

The Dummy classifier has been taken as a baseline for comparison.

```{r logistic_model_build, echo=FALSE}
# Set working directory as this directory
setwd(dirname(rstudioapi::getSourceEditorContext()$path))

# Load the dataset and pre-process it
bank_logistic <- read.csv("./datasets/BankChurners.csv", sep = ",")
bank_logistic <- bank_logistic[, -c(1, 3, 5, 6, 9, 10, 14, 16, 17, 21, 22, 23)]
bank_logistic$Attrition_Flag <- ifelse(bank_logistic$Attrition_Flag == "Attrited Customer", 1, 0)

# Convert all categorical variables to factors and reorder the levels
bank_logistic$Gender <- as.factor(bank_logistic$Gender)
bank_logistic$Marital_Status <- as.factor(bank_logistic$Marital_Status)
bank_logistic$Marital_Status <- forcats::fct_relevel(bank_logistic$Marital_Status,
                                            "Unknown",
                                            "Single",
                                            "Married",
                                            "Divorced")

bank_logistic$Income_Category <- as.factor(bank_logistic$Income_Category)
bank_logistic$Income_Category <- forcats::fct_relevel(bank_logistic$Income_Category,
                                             "Unknown",
                                             "Less than $40K",
                                             "$40K - $60K",
                                             "$60K - $80K",
                                             "$80K - $120K",
                                             "$120K +")

# Override the Total_Trans_Amt variable with its log !!!
bank_logistic$Total_Trans_Amt <- log(bank_logistic$Total_Trans_Amt)

# Standardization (optional) all columns except response and categorical
bank_logistic[, -c(1, 2, 3, 4)] <- scale(bank_logistic[, -c(1, 2, 3, 4)])

# Converting Months_Inactive_12_mon to a factor
bank_logistic$Months_Inactive_12_mon <- as.factor(bank_logistic$Months_Inactive_12_mon)
levels(bank_logistic$Months_Inactive_12_mon) <- c("0", "1", "2", "3", "4", "5", "6+")

# Joining toghether the levels after 4 months
bank_logistic$Months_Inactive_12_mon <- fct_collapse(bank_logistic$Months_Inactive_12_mon,
                                            "4+" = c("4", "5", "6+"))

# Removing from the dataset the Marital_Status and Income_Category variables
bank_logistic <- bank_logistic[, -c(3, 4)]

# Rebuiding and checking the model
simple_logistic_model <- learn_logistic(bank_logistic)

```

### Results on the original dataset

On the given dataset, the built logistic model summary is the following:

```{r logistic_model_summary}
summary(simple_logistic_model)
```

The results of the ANOVA test are the following:

```{r logistic_model_anova}
anova(simple_logistic_model, test = "Chisq")
```

As its possible to see all the contribute in decreasing the deviance of the model, and they are all statistically significant.\

For what concerns the effectiveness metrics, we measured the following results on the original dataset:

```{r logistic model_results, message=FALSE, warning=FALSE}
logistic_results <- assess_logistic(simple_logistic_model, bank_logistic)
```

And similar results for the k-fold cross validation:

```{r logistic_model_cv_results, message=FALSE, warning=FALSE}
cv_logistic(bank_logistic)
```

From the results we can clearly see that the model is overall performing well. The accuracy is consistently over $90\%$ on all the folds, but this is not too surprising given the unbalance nature of the model. Good values have however been reached for the AUC and the FPR, with the worst metric being the FNR which falls just below $50\%$. The AIC and BIC values are also very low, which is a good sign for the model.

### Results on the synthetic dataset (ROSE)

As noticed above, the dataset is characterized by a strong class imbalance:
```{r}
table(bank_logistic$Attrition_Flag)
```

```{r,echo=FALSE}
cat("Attrited customers (rare class): ",sum(bank_logistic$Attrition_Flag==1))
cat("Existing customers (maj class): ",sum(bank_logistic$Attrition_Flag==0))
cat("Proportion of attrited:",
    sum(bank_logistic$Attrition_Flag==1)/sum(table(bank_logistic$Attrition_Flag))*100,"%")
```

Let's apply *ROSE* package:
```{r}
library(ROSE)
bank_logistic_balanced<- ROSE(Attrition_Flag~.,data=bank_logistic,seed = 123)$data
```

```{r}
table(bank_logistic_balanced$Attrition_Flag)
```

```{r,echo=FALSE}
cat("Attrited customers (rare class): ",sum(bank_logistic_balanced$Attrition_Flag==1))
cat("Existing customers (maj class): ",sum(bank_logistic_balanced$Attrition_Flag==0))
cat("Proportion of attrited:",
    sum(bank_logistic_balanced$Attrition_Flag==1)/sum(table(bank_logistic_balanced$Attrition_Flag))*100,"%")
```

Now we can learn a logistic regression model on the new balanced dataset:

```{r}
ROSE_logistic_model <- learn_logistic(bank_logistic_balanced)
```

For what concerns the effectiveness metrics on the original dataset:

```{r, message=FALSE, warning=FALSE}
ROSE_logistic_results<- assess_logistic(ROSE_logistic_model, bank_logistic_balanced)
```

Instead, by computing a 10-fold CV:
```{r, message=FALSE, warning=FALSE}
cv_logistic(bank_logistic_balanced)
```
**Comment:** the accuracy of this model, as expected, is lower than one of the logistic model learnt on the unbalanced dataset. However, the difference with respect to the dummy classifier becomes definitely more evident. Regarding the AUC score, even its value is slightly lower than before, it still showcases how good is the fit of our model. The metric that really improves after applying ROSE is the FNR: the model learnt on the unbalanced dataset had an average FNR of 44.11%, while now it drops around 17.87%. Conversely, FPR increases from 3.02% to 17.85%, but since we don't know anything about the costs of the errors, we considered it better to have more balanced metrics for FPR and FNR.

## Penalized regression
### Results on the original dataset
### Results on the synthetic dataset (ROSE)

## GAM/Splines
### Results on the original dataset
### Results on the synthetic dataset (ROSE)

## Decision Trees ?

## Ensemble Methods

The last class of methods we used to model the `Attrition_Flag` variable is ensamble methods, in particular we focussed on AdaBoost and Random Forest.\
The first model we built is an AdaBoost model on the whole dataset, which on its own achieved some great results. Then we proceeded by removing the variables considered not statistically significant in more complex models like `GAM`. This slight modification didn't much modify the accuracy of the model, which is always on the order of about $\sim90\%$.\
The final model has been built using the following variables:

* `Gender`: the gender of the customer
* `Total_Relationship_Count`: the total number of products held by the customer
* `Months_Inactive_12_mon`: the number of months inactive in the last 12 months
* `Contacts_Count_12_mon`: the number of contacts in the last 12 months
* `Total_Revolving_Bal`: the total revolving balance on the credit card
* `Total_Trans_Amt`: the total transaction amount in the last 12 months
* `Total_Trans_Ct`: the total transaction count in the last 12 months
* `Total_Ct_Chng_Q4_Q1`: the change in transaction count from Q4 to Q1
* `Marital_Status`: the marital status of the customer
* `Income_Category`: the income category of the customer

The same pre-processing steps of the `GLM` model were performed, slightly modifying classes or taking logarithmic values and converting the `Months_Inactive_12_mon` variable to a factor.\
The effectiveness metrics used to assess the model are:

* Accuracy
* AUC
* FPR (False Positive Rate)
* FNR (False Negative Rate)
* Confusion matrix
* Variable importance

The dummy classifier has been taken as a baseline for comparison.

```{r ada_model_build, echo=FALSE}
setwd(dirname(rstudioapi::getSourceEditorContext()$path))

# Load the dataset and pre-process it
bank_ensamble <- read.csv("datasets/BankChurners.csv", sep = ",")
bank_ensamble <- bank_ensamble[, -c(1, 22, 23)]
#bank$Attrition_Flag <- ifelse(bank$Attrition_Flag == "Attrited Customer", 1, 0)
# Convert Attrition_Flag to a binary factor
bank_ensamble$Attrition_Flag <- factor(bank_ensamble$Attrition_Flag == "Attrited Customer", levels = c(FALSE, TRUE))

# If "Attrited Customer" is TRUE, it will be coded as 1, and other values will be coded as 0


# Convert all categorical variables to factors and reorder the levels
bank_ensamble$Gender <- as.factor(bank_ensamble$Gender)
bank_ensamble$Income_Category <- fct_collapse(bank_ensamble$Income_Category,
                                     "Less than 120K" = c("Unknown",
                                                          "Less than $40K",
                                                          "$40K - $60K",
                                                          "$60K - $80K",
                                                          "$80K - $120K"),
                                     "More than 120K" = c("$120K +"))

# Changing the levels of Marital_Status in either married or not married
bank_ensamble$Marital_Status <- fct_collapse(bank_ensamble$Marital_Status,
                                    "Married" = c("Married"),
                                    "Not Married" = c("Divorced",
                                                      "Single",
                                                      "Unknown"))
# Converting Months_Inactive_12_mon to a factor
bank_ensamble$Months_Inactive_12_mon <- as.factor(bank_ensamble$Months_Inactive_12_mon)
levels(bank_ensamble$Months_Inactive_12_mon) <- c("0", "1", "2", "3", "4", "5", "6+")

# Joining together the levels after 4 months
bank_ensamble$Months_Inactive_12_mon <- fct_collapse(bank_ensamble$Months_Inactive_12_mon,
                                            "4+" = c("4", "5", "6+"))

bank_ensamble$Education_Level <- as.factor(bank_ensamble$Education_Level)
bank_ensamble$Marital_Status <- as.factor(bank_ensamble$Marital_Status)
bank_ensamble$Income_Category <- as.factor(bank_ensamble$Income_Category)
bank_ensamble$Card_Category <- as.factor(bank_ensamble$Card_Category)
# Override the Total_Trans_Amt variable with its log !!!
bank_ensamble$Total_Trans_Amt <- log(bank_ensamble$Total_Trans_Amt)
bank_ensamble <- bank_ensamble[, -c(2, 4, 5, 8, 9, 13, 15, 16, 20)]

# Actual model building
set.seed(1234)
index <- createDataPartition(bank_ensamble$Attrition_Flag , p =0.8, list = FALSE)

train_bank_ensamble <- bank_ensamble[index,]
test_bank_ensamble <- bank_ensamble[-index,]
boost_model <- learn_boost(train_bank_ensamble)
rf_model <- learn_rf(train_bank_ensamble)
```

### Results on the original dataset
A summary-like output of the model doesn't exist, but we can still assess the model performance using the metrics described above.

First we show the results relative to a single run of the model on the dataset:

```{r ada_model_summary}
boost_results <- assess_boost(boost_model, test_bank_ensamble)

```

Then the results on a 10-fold cross validation:

```{r ada_model_cv_results}
cv_boost_results <- cv_boost(bank_ensamble)

```

As we can see from these results, AdaBoost is performing pretty well, having a consistent accuracy of over $90\%$ and a good AUC score. The FPR and FNR are also very low, keeping them consistently under $20\%$. Not having an AIC or BIC-like score, we can't really compare the model to the previous ones, but the results on classification are much better than the ones above, in particular with respect to the simple logistic regression.\

Passing to Random Forest, we perform the same analysis:

```{r rf_model_summary}
rf_results <- assess_rf(rf_model, test_bank_ensamble)

```

```{r rf_model_cv_results}
cv_rf_results <- cv_rf(bank_ensamble)

```

The results are very similar to the ones of AdaBoost, with the only difference being a slightly lower accuracy and AUC score. The FPR and FNR are also very low, keeping them consistently under $20\%$. A consistent note should be pointed that on the fact that performing cross validation, the average FNR decreases to below $5\%$, demonstrating the adaptive power of Random Forest also on unbalanced data.\


### Results on the synthetic dataset (ROSE)
    
    
# Interpretations/Conclusions

